Whats reported in the news?

### 2018-03-19 paper/docs/04_Modelresults_50.Rmd
change styling of figures

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 5,
dpi = 600)
```

@@

The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting. For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.

@@

###### Normalization

@@

polls <- table_long %>%
  mutate(yearmonth = calculate_month(month(Datum),year(Datum)),
         yearweek = calculate_week(week(Datum), year(Datum)))

## Monthly
# polls_monthly <- polls %>%
#   group_by(yearmonth,party) %>%
#   summarise(mean_val = mean(value, na.rm=T)) %>%
#   ungroup() %>%
#   filter(!party %in% c("Piraten", "Sonstige")) %>%
#   filter(mean_val != "NaN") %>%
#   mutate(mean_val = normalize_data(mean_val)) %>%
#   select(party, yearmonth, mean_val) %>%
#   spread(party, mean_val) %>%
#   filter(yearmonth > as.Date("2017-05-01"))

polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  filter(yearmonth < as.Date("2018-03-01")) %>%
  mutate(AfD = normalize_data(AfD),
         FDP = normalize_data(FDP),
         Grüne = normalize_data(Grüne),
         Linke = normalize_data(Linke),
         SPD = normalize_data(SPD),
         Union = normalize_data(Union))

@@

B)
```{r}
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

@@

      ### Plot Corr ##
      ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", ...) +
        geom_text(size = 3.5, color = col[5]) +
        viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "Cross-Correlation / Polls vs. Sentiment Value",
             ...)
}
```

@@

plot_ccf(corr1, corr2)
```

##### 3.1.2. By Media
```{r eval=FALSE, include=FALSE}
for (i in unique(group2$site)) {

@@

  p1 <- ggplot() +
    geom_col(data=plot1, aes(yearmonth, sentiment_n,
                             group = topic_name,
                             fill = topic_name),
             position = "dodge",
             alpha = 0.5) +
    scale_fill_manual(values = col) +

    geom_line(data=plot1, aes(yearmonth, 
                              sentiment_n,
                              group = topic_name,
                              color = topic_name),
              show.legend = F) +
    scale_color_manual(values = col) +
    guides(fill = guide_legend(ncol=3)) +

@@

  p2 <- ggplot() +
    geom_col(data = plot2,
             aes(yearmonth, sentiment_n, 
                 group = topic_name,
                 fill = topic_name),
             alpha = 0.5,
             position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +

@@

##### 3.2.1. CDU
```{r fig.height=12, fig.width=10}
filters <- paste("CDU","CSU","Great Coalition", sep="|")

>>>>

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 8, height = 6,
dpi = 600)
```

@@

polls <- table_long %>%
  mutate(yearmonth = calculate_month(month(Datum),year(Datum)),
         yearweek = calculate_week(week(Datum), year(Datum))) 
```

```{r include=FALSE}
p <- polls %>%
  filter(yearmonth > as.Date("2017-01-01")) %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  ggplot(aes(Datum, value, 
             group = party,
             color = party)) +
  geom_line() +
  scale_color_manual(values =  c("deepskyblue", "gold", "limegreen", "deeppink", "red", "black")) +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels=date_format("%b", tz="CET")) +
    geom_vline(xintercept = as.Date("2017-09-24"), 
             linetype = 2, color = col[3]) +
  labs(x="", y="", color="",
       title = "",
       caption = "source: infratest dimap") +
    guides(color = guide_legend(nrow = 1,
                                label.theme = element_text(size = 6,
                                                           angle=0))) +
  theme(axis.text = element_text(size=6),
        legend.position = "bottom")

ggsave(filename = "../figs/polls.png", plot = p, width = 6, height = 4, dpi = 600)
```

![Poll Results](../figs/polls.png)
###### Normalization 
The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting. For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.

@@

@@

```{r}
polls_monthly <- polls %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(!party %in% c("Piraten", "Sonstige")) %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val) %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  filter(yearmonth < as.Date("2018-03-01")) %>%
  mutate(AfD = normalize_data(AfD),
         FDP = normalize_data(FDP),
         Grüne = normalize_data(Grüne),
         Linke = normalize_data(Linke),
         SPD = normalize_data(SPD),
         Union = normalize_data(Union))

@@

B) Normalize each time series by its own.

```{r}
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w)

@@

      ### Plot Corr ##
      ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", ...) +
        geom_text(size = 3.5, color = col[5]) +
        viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "",
             ...)
}
```

@@

p <- plot_ccf(corr1, corr2, alpha = 0.8,
              subtitle = "Election polls vs. topic sentiment value (monthly)")

ggsave(filename = "../figs/ccf.png", plot = p,
       height = 6, width = 8)
```

![Cross-correlation](../figs/ccf.png)
##### 3.1.2. By Media
```{r eval=FALSE, include=FALSE}
for (i in unique(group2$site)) {

@@

  p1 <- ggplot() +
    # geom_col(data=plot1, aes(yearmonth, sentiment_n,
    #                          group = topic_name,
    #                          fill = topic_name),
    #          position = "dodge",
    #          alpha = 0.5) +
    # scale_fill_manual(values = col) +

    geom_line(data=plot1, aes(yearmonth, 
                              sentiment_n,
                              group = topic_name,
                              color = topic_name),
              show.legend = F) +
    #scale_color_manual(values = col) +
    guides(fill = guide_legend(ncol=3)) +

@@

  p2 <- ggplot() +
    # geom_col(data = plot2,
    #          aes(yearmonth, sentiment_n, 
    #              group = topic_name,
    #              fill = topic_name),
    #          alpha = 0.5,
    #          position = "dodge") +
    # scale_fill_manual(values = col) +
    # scale_color_manual(values = col) +

@@

##### 3.2.1. CDU
```{r fig.height=12, fig.width=10}
filters <- paste(":", sep="|")
